Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-22 ms.tex
better side-by-side comparison

\begin{figure*}
\gridline{\fig{all_var_azlab_mult_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Baseline}
\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
\caption{Allan variance for background-subtracted rectangular photometry on the S01 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{all_var_azlab06_mult_exp_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Multi-Exposure Baseline}
\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
\caption{Allan variance for background-subtracted rectangular photometry on the Asic Dewar versus the GL dewar.
%Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
\end{figure*}
